Testing gene methylation enrichment analysis approaches using simulated data

### 2023-12-27 figs/GSE158422_simulate020.Rmd
roll back gene name fix

#new.hgnc.table <- getCurrentHumanMap()
new.hgnc.table <- readRDS("new.hgnc.table.rds")
fix <- checkGeneSymbols(gt$gene,map=new.hgnc.table)
fix2 <- fix[which(fix$x != fix$Suggested.Symbol),]
length(unique(fix2$x))
gt$gene <- fix$Suggested.Symbol

@@

num_dm_sets=50
sims=50

>>>>

#new.hgnc.table <- getCurrentHumanMap()
#new.hgnc.table <- readRDS("new.hgnc.table.rds")
#fix <- checkGeneSymbols(gt$gene,map=new.hgnc.table)
#fix2 <- fix[which(fix$x != fix$Suggested.Symbol),]
#length(unique(fix2$x))
#gt$gene <- fix$Suggested.Symbol

@@

num_dm_sets=50
sims=20
